---
title: "Wellennachweis - Pressverbindung"
author: "Quentin Huss, Nadine Schulz"
date: "14.06.2023"
output: pdf_document
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE}

```




# 0 gegebene Größen  
## Geometrie Stelle `r z_Koordinate` mm der `r Welle`  
Wellendurchmesser:  
$$d_w = `r dw`mm$$
 
## Beanspruchung  

Biegemittelspannung:

$$
\sigma_{bm} = 0 \dfrac{N}{mm^{2}}
$$ Biegeausschlagspannung:

$$
\sigma_{ba} = `r round(sigma_max, 3)` \dfrac{N}{mm^{2}}
$$

Torsionsmittelspannung:

$$
\tau_{tm} = 0 \dfrac{N}{mm^{2}}
$$

Torsionsausschlagspannung:

$$
\tau_{ta} = `r round(tau_max, 3)` \dfrac{N}{mm^{2}}
$$

# 1 Bauteilwechselfestigkeiten  
## Kerbwirkungszahlen  
\begin{center}
$\beta_{\sigma_b} = `r beta_sigma`$ 
  
$\beta_{\tau} = `r beta_tau`$  
\end{center}  

## Gesamteinflussfaktoren  
\begin{center}

$K_{\sigma ,b} = `r K_ges_sigma`$  

$K_{\tau} = `r K_ges_tau`$

\end{center}

## Bauteilwechselfestigkeit  
\begin{center}

$\sigma_{bWK} = `r sigma_bWK`\ \dfrac{N}{mm^{2}}$

$\tau_{tWK} = `r tau_bWK`\ \dfrac{N}{mm^{2}}$

\end{center}

\pagebreak

# 2 Bauteilfließgrenzen  
\begin{center}  
$\sigma_{bFK} = `r sigma_bFK`\ \dfrac{N}{mm^{2}}$  

$\tau_{tFK} = `r tau_tFK`\ \dfrac{N}{mm^{2}}$  
\end{center}  

# 3 Gestaltfestigkeit  
\begin{center}
$\sigma_{bADK} = `r sigma_bADK`\ \dfrac{N}{mm^{2}}$  

$\tau_{tADK} = `r tau_tADK`\ \dfrac{N}{mm^{2}}$  
\end{center}  

# 4 Sicherheiten  
\begin{center}
$S_F = `r S_F`$  

$S_D = `r S_D`$
\end{center}