---
title: "Wellennachweis - Zahnwelle"
output: pdf_document
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
- \usepackage{tikz}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE}

```


# 0 gegebene Größen  
## Geometrie Stelle `r z_Koordinate` mm der `r Welle`  
Wellendurchmesser:  
$$d_w = `r dw`mm$$
 
## Beanspruchung

Biegemittelspannung:

$$
\sigma_{bm} = 0 \dfrac{N}{mm^{2}}
$$ Biegeausschlagspannung:

$$
\sigma_{ba} = `r round(sigma_max, 3)` \dfrac{N}{mm^{2}}
$$

Torsionsmittelspannung:

$$
\tau_{tm} = 0 \dfrac{N}{mm^{2}}
$$

Torsionsausschlagspannung:

$$
\tau_{ta} = `r round(tau_max, 3)` \dfrac{N}{mm^{2}}
$$

# 1 Bauteilwechselfestigkeiten

## Kerbwirkungszahlen

$$\beta_{\sigma_b} = `r round(beta_sigma, 3)`$$

$$\beta_{\tau} = `r round(beta_tau, 3)`$$

## Gesamteinflussfaktoren

$$K_{\sigma ,b} = `r round(K_ges_sigma, 3)`$$

$$K_{\tau} = `r round(K_ges_tau, 3)`$$

## Bauteilwechselfestigkeit

$$\sigma_{bWK} = `r round(sigma_bWK, 3)` \dfrac{N}{mm^{2}}$$

$$\tau_{tWK} = `r round(tau_bWK, 3)` \dfrac{N}{mm^{2}}$$

# 2 Bauteilfließgrenzen

$$\sigma_{bFK} = `r round(sigma_bFK, 3)` \dfrac{N}{mm^{2}}$$

$$\tau_{tFK} = `r round(tau_tFK, 3)` \dfrac{N}{mm^{2}}$$

# 3 Gestaltfestigkeit

$$\sigma_{bADK} = `r round(sigma_bADK, 3)` \dfrac{n}{mm^{2}}$$

$$\tau_{tADK} = `r round(tau_tADK, 3)` \dfrac{N}{mm^{2}}$$

# 4 Sicherheiten

$$S_F = `r S_F`$$

$$S_D = `r S_D`$$
